### 2022-11-21 Draft_GFC.tex
21/11/2022

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{-.3in}%
\addtolength{\topmargin}{-.8in}%

\usepackage{amsmath,amssymb,amsthm,amsfonts,amstext,amsbsy,amscd,stmaryrd}
\usepackage{amssymb,amsmath,comment,subcaption,graphicx}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{cancel}
\usepackage{tikz}
\usepackage{subcaption} 
\usetikzlibrary{patterns}
\usepackage{xcolor}
\usepackage{bbm}
\usepackage{float}
\usepackage{color}
\usepackage{relsize}
\newcommand{\modif}[1]{{\begin{modification}#1\end{modification}}}
\newcommand{\ele}[1]{{\color{red}#1}}
%\UseRawInputEncoding
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{mathrsfs}
\newcommand{\rmd}{{\mathrm{d}}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Z}{\mathbb{Z}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\E}{\operatorname{\mathbb{E}}}
\newcommand{\Var}{\operatorname{Var}}
\newcommand{\Cov}{\mathrm {Cov}}
\newcommand{\rme}{{\rm e}}
\renewcommand{\tilde}{\widetilde}
\renewcommand{\hat}{\widehat}
\newcommand{\TC}{\mathrm{TC}}
\newcommand{\TaC}{\mathrm{TaC}}
\newcommand{\LTC}{\mathrm{LTC}}
\newcommand{\LP}{\mathrm{LP}}
\newcommand{\Per}{\mathrm{Per}}
\theoremstyle{Theorem}
\newtheorem{Theorem}{Theorem}[section]
\newtheorem{Corollary}[Theorem]{Corollary}
\newtheorem{Lemma}[Theorem]{Lemma}
\newtheorem{Proposition}[Theorem]{Proposition}
\newtheorem{Definition}[Theorem]{Definition}
\newtheorem{remark}{Remark}
\renewcommand{\labelitemi}{\textperiodcentered}
\allowdisplaybreaks
\usepackage{ifpdf}
\ifpdf
\else
\usepackage{graphicx}
\DeclareGraphicsExtensions{.eps,.jpg,.png}
\fi
\usepackage{epstopdf}

@@

\section{Mathematical framework}\label{section1}
\subsection{Construction of the binary image}\label{construction}
\paragraph{Square tiling}
Let $m$ be an integer with $m \geq 2$. Without loss of generality, we consider our observation window as the unit square $S = [0,m]^{2}$ and  we divide our window into $m^{2}$ pairwise disjoint squares. We denote by $G_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \mathbb{Z}^{2} $ the set of point in $S$ with interger coordinates and for $x \in G_{m}$, we define $C_{m}(x)$ as
\begin{equation*}
C_{m}(x) \, := \,x + \text{\larger[1]{$[$}}0, 1 \text{\larger[1]{$]$}}^{2} \subset S.
\end{equation*}
The $C_{m}(x)$ will be referred to as \textit{cells}, to ease up the notations we denote by $x = (x_1, x_2)$ with $x_1, x_2 \in \{0,\ldots, m-1\}$ and $e_1$, $e_{2}$ the element of the canonical base of $\mathbb{R}^{2}$.
We denote by $\mathbb{E}^{(1)}_{m}, \; \mathbb{E}^{(2)}_{m} $ the set of vertical and horizontal edges in $\mathring{S} = (0,m)^{2}$, and $\mathbb{E}_{m} = \mathbb{E}^{(1)}_{m} \cup \mathbb{E}^{(2)}_{m}$ each $w \in \mathbb{E}_{m}$ is a segment of length $1$.
Figure \ref{fig1} shows an example of a square tiling with $m = 4$.
\begin{figure}[h]
\begin{center}
\begin{tikzpicture}[scale = 0.5]
  \draw[step = 1cm, black, thick](0,0) grid (4,4);
\draw[pattern=north west lines, pattern color=blue] (0,0) rectangle (1,1);
\draw[pattern=north west lines, pattern color=blue] (3,1) rectangle (2,2);
\foreach \x in {0,1,2,3}{
  \foreach \y in {0,1,2,3}{
  \draw[fill = red] (\x,\y) circle (2pt);
  } 
}
\end{tikzpicture}
\end{center}
\vspace{-0.25cm}
\caption{Tiling with squares for $m = 4$ and associated cells $C_{4}(0,0)$ and $C_{4}(2,1)$ (blue stripes) and red point of $G_{m}$.}
\label{fig1}
\end{figure}

\paragraph{Discrete setting}
Using the previous square tiling, we write $S =  \underset{x \in G_m}{\cup}  C_{m}(x)$. We assume to observe $\left(X_{\scriptscriptstyle x}\right)_{x \in G_{m}}$, which we assume coincides with values of a stationary random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$. The stationarity hypothesis means that for all $h \in \mathbb{Z}^{2}$, 
$$\left(X_{x+h}; x \in \mathbb{Z}^{2} \right)\overset{fdd}{=} \left(X_{\scriptscriptstyle x}; x \in \mathbb{Z}^{2} \right),$$ where $fdd$ denotes finite-dimensional distributions. \\
We denote by $\rho(x) :=\text{Cov}\left(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle x}\right), \; x \in \mathbb{Z}^{2}$, the covariance function of $X$.
\vspace{-1.5cm}
\begin{figure}[H]
    {\includegraphics[scale=0.25]{GaussianUn.pdf}}
    {\includegraphics[scale=0.25]{GaussianZUn.pdf}}
    {\includegraphics[scale=0.25]{GaussianZZZUn.pdf}}
    \vspace{-2cm}
 \caption{Generations of Gaussian random field with covariance $\rho(x) = e^{-\kappa||x||^{2}}$ with $m = 1024$, and different values for $\kappa$, from left to right $\kappa = 0.01, 0.1, 1$, using the Matlab function \textit{stationary Gaussian process} \cite{MATLAB}.}
\label{fig22}
\end{figure}
Let us consider a threshold parameter $t \in \mathbb{R}$. We introduce the associated binary image $Z^{\scriptscriptstyle (m)}_{t} = \left(\mathbbm{1}_{\left\{X_x \geq t\right\}} \right)_{x \in G_{m}}$, each cell $C_{m}(x)$ is associated to black or white according to whether $Z^{\scriptscriptstyle (m)}_{t} (x) = 0$ or $Z^{\scriptscriptstyle (m)}_{t}(x)~= 1$. 
\subsection{Perimeter of a binary image}\label{methods}
For $t \in \mathbb{R}$,let $Z^{\scriptscriptstyle (m)} = Z^{\scriptscriptstyle (m)}_{t}$ be the  binary image  $Z^{\scriptscriptstyle (m)}$ at that given threshold $t \in \mathbb{R}$. Following  the approach  presented in \cite{HermineAgnes},  for each edge $w \in \mathbb{E}_{m}$, we aim to know if  $w$ contributes  to the perimeter of the black component of $Z$. Making use of the additive nature of the perimeter, one can start by computing the oriented perimeter given each direction, horizontal and vertical. Let us consider the edge $w_{i}(x) := \left(x, x+e_{i}\right)$ with $i \in \{1,2\}$, $w_{i}(x)$ belongs to $C_{m}(x) \cap C_{m}(x-e_{j})$ with $i,j \in \{1,2\}$ and $i \neq j$ as soon as $w_{i}(x) \subset  \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}$.
\begin{figure}[H]
\begin{center}
\begin{tikzpicture}
    [
        box/.style={rectangle,draw=black,thick, minimum size=1cm},
    ]

@@

% \section{Statistics of the perimeter} 
\section{First moment}

@@

We assume that $\left(X_x \right)_{x \in G_{m}}$ is a stationary Gaussian centered with unit variance random field let us denote \linebreak by  $\rho(e_i) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) \in~[-1, 1]$. The expected value of the perimeter in \eqref{eq:6} is  given \linebreak by $$\mathbb{E}\left(\mathcal{P}_{m}(t)\right) = m(m-1)\sum_{1}^{2}\mathbb{E}\left(f^{(i)}(t) \right)$$  and

@@

\left\{ x \in G_{m}; w_{i}(x) \in \mathbb{E}^{\scriptscriptstyle  (i)}_{m}\right\} & = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, (x, x+e_i)\subset (0,m)^{2} \right\} \\ 

@@

\textcolor{blue}{Decreasing behavior for all level $t$.}

@@

 \text{if} \hspace{0.5cm} \tilde{\rho}(e_i) < \bar{\rho}(e_i) \hspace{0.5cm} \text{then} \hspace{0.5cm}\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(t)\right) > \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(t)\right).

@@

Let $x\in(-1,1)$ and $f: x \mapsto \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right)\right)$ we consider $a,b  \in (-1,1)$, such that $a > b$, 

@@

f(a) - f(b) = \mathbb{E}\left(\Phi_{\pi_{V}}\left(2t + \sqrt{2(1-a)}|N|\right) - \Phi\left(2t + \sqrt{2(1-b)}|N|\right)\right) + \mathbb{E}\left(\Phi\left(2t - \sqrt{2(1-b)}|N|\right)- \Phi\left(2t - \sqrt{2(1-a)}|N|\right)\right) \\ 
= \underbrace{\mathbb{E}\left(\Phi\left(2t + \sqrt{2(1-a)}|N|\right) - \Phi\left(2t + \sqrt{2(1-b)}|N|\right)\right)}_{< 0} + \mathbb{E}\left(\Phi\left(-2t + \sqrt{2(1-a)}|N|\right)- \Phi\left(-2t + \sqrt{2(1-b)}|N|\right)\right) \\
= \underbrace{\mathbb{E}\left(\Phi\left(2t + \sqrt{2(1-a)}|N|\right) - \Phi\left(2t + \sqrt{2(1-b)}|N|\right)\right)}_{< 0} + \underbrace{\mathbb{E}\left(\Phi\left(-2t + \sqrt{2(1-a)}|N|\right)- \Phi\left(-2t + \sqrt{2(1-b)}|N|\right)\right)}_{<  0} \\
= \underbrace{\mathbb{E}\left(\Phi\left(2t + \sqrt{2(1-a)}|N|\right) - \Phi\left(2t + \sqrt{2(1-b)}|N|\right)\right) + \mathbb{E}\left(\Phi\left(-2t + \sqrt{2(1-a)}|N|\right)- \Phi\left(-2t + \sqrt{2(1-b)}|N|\right)\right)}_{<  0}
Thus if $a > b$

@@

\mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right)\right) <  \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right)

@@

\textcolor{blue}{reorient toward Github for illustrations.}
\section{Covariance of the perimeter for two thresholds}

@@

& = \sum_{x_1=2-m}^{m-1} \sum_{x_2 = 1-m}^{m-2} \left(m-|x_1| - \mathbbm{1}_{x_{1} < 0}\right)\left(m-|x_2|-\mathbbm{1}_{x_{2} \geq 0}\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(x) \right)

@@

1 \leq x_2 \leq m-1 \\
1 \leq y_2 \leq m-1 
\end{array}\right. & \implies

@@

\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (1)}(s) \right) &  = \sum_{z_{\scriptscriptstyle 1} = \left(1-m\right)}^{m-1}\sum_{z_{\scriptscriptstyle 2}=\left(2-m\right)}^{m-2}\left(m -|z_{1}|\right)\left(m - 1- |z_{2}|\right) \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(z) \right) 

@@

\end{align*}}Let us assume that $|\rho(e_1)| < 1$, the Cholesky decomposition of $\Sigma_{i}(x)$ allows us to get the expression of the Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x},S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \right)$ in a new basis $\left(U,V,W,Z\right)$ with $\left(U, V, W, Z\right) \sim \mathcal{N}\left(0,I_{4}\right)$. We get the following decomposition \\ 

@@

& = \mathbbm{1}_{\left\{ 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W  - |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \leq \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z\leq 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W + |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \right\}}

@@

&\hspace{-6.5cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}| \leq |\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}|\right\}}\mathbbm{1}_{\left\{ 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W  - |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \leq \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z\leq 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W + |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \right\}}\right)\\

@@

&\hspace{-6cm} \left. \left|\Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s + \left( \pi^{\scriptscriptstyle(-, i)}_{U}(x)- \pi^{\scriptscriptstyle(+, i)}_{U}(x)\right) U + \left(\pi^{\scriptscriptstyle(-, i)}_{V}(x)- \pi^{\scriptscriptstyle(+, i)}_{V}(x)\right)V + \left(\pi^{\scriptscriptstyle(-, i)}_{W}(x) - \pi^{\scriptscriptstyle(+, i)}_{W}(x)\right) W \right) \right. \right.  \nonumber \\
& \hspace{-5cm}\left. \left.  - \Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s - \left( \pi^{\scriptscriptstyle(-, i)}_{U}(x)+ \pi^{\scriptscriptstyle(+, i)}_{U}(x)\right) U - \left(\pi^{\scriptscriptstyle(-, i)}_{V}(x)+ \pi^{\scriptscriptstyle(+, i)}_{V}(x)\right)V   - \left( \pi^{\scriptscriptstyle(+, i)}_{W}(x) +  \pi^{\scriptscriptstyle(-, i)}_{W}(x) \right)W \right)  \right| \right)

@@

\begin{tabularx}{\textwidth}{|l| l|X|}

@@

$\Delta \rho(x)$ & \hspace{4cm}$\rho(x-e_1)-\rho(x)$ & $O(\rho(x))$ \\ \hline

>>>>

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{-.3in}%
\addtolength{\topmargin}{-.8in}%
\usepackage{amsmath,amssymb,amsthm,amsfonts,amstext,amsbsy,amscd,stmaryrd}
\usepackage{amssymb,amsmath,comment,subcaption,graphicx}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{cancel}
\usepackage{tikz}
\usepackage{subcaption} 
\usetikzlibrary{patterns}
\usepackage{xcolor}
\usepackage{bbm}
\usepackage{float}
\usepackage{color}
\usepackage{relsize}
\newcommand{\modif}[1]{{\begin{modification}#1\end{modification}}}
\newcommand{\ele}[1]{{\color{red}#1}}
%\UseRawInputEncoding
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{mathrsfs}
\newcommand{\rmd}{{\mathrm{d}}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Z}{\mathbb{Z}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\E}{\operatorname{\mathbb{E}}}
\newcommand{\Var}{\operatorname{Var}}
\newcommand{\Cov}{\mathrm {Cov}}
\newcommand{\rme}{{\rm e}}
\renewcommand{\tilde}{\widetilde}
\renewcommand{\hat}{\widehat}
\newcommand{\TC}{\mathrm{TC}}
\newcommand{\TaC}{\mathrm{TaC}}
\newcommand{\LTC}{\mathrm{LTC}}
\newcommand{\LP}{\mathrm{LP}}
\newcommand{\Per}{\mathrm{Per}}
\theoremstyle{Theorem}
\newtheorem{Theorem}{Theorem}[section]
\newtheorem{Corollary}[Theorem]{Corollary}
\newtheorem{Lemma}[Theorem]{Lemma}
\newtheorem{Proposition}[Theorem]{Proposition}
\newtheorem{Definition}[Theorem]{Definition}
\newtheorem{remark}{Remark}
\renewcommand{\labelitemi}{\textperiodcentered}
\allowdisplaybreaks
\usepackage{ifpdf}
\ifpdf
\else
\usepackage{graphicx}
\DeclareGraphicsExtensions{.eps,.jpg,.png}
\fi
\usepackage{epstopdf}
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}

@@

\section{Mathematical framework}\label{section1}
\subsection{Construction of the binary image}\label{construction}
\paragraph{Square tiling}
Let $m$ be an integer with $m \geq 2$. Without loss of generality, we consider our observation window as the unit square $S = [0,m]^{2}$ and  we divide our window into $m^{2}$ pairwise disjoint squares. We denote by $\mathbb{G}_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \mathbb{Z}^{2} $ the set of point in $S$ with interger coordinates and for $x \in \mathbb{G}_{m}$, we define $C_{m}(x)$ as
\begin{equation*}
C_{m}(x) \, := \,x + \text{\larger[1]{$[$}}0, 1 \text{\larger[1]{$]$}}^{2} \subset S.
\end{equation*}
The $C_{m}(x)$ will be referred to as \textit{cells}, to ease up the notations we denote by $x = (x_1, x_2)$ with $x_1, x_2 \in \{0,\ldots, m-1\}$ and $e_1$, $e_{2}$ the element of the canonical base of $\mathbb{R}^{2}$.
We denote by $\mathbb{E}^{(1)}_{m}, \; \mathbb{E}^{(2)}_{m} $ the set of vertical and horizontal edges in $\mathring{S} = (0,m)^{2}$, and $\mathbb{E}_{m} = \mathbb{E}^{(1)}_{m} \cup \mathbb{E}^{(2)}_{m}$ each $w \in \mathbb{E}_{m}$ is a segment of length $1$.
Figure \ref{fig1} shows an example of a square tiling with $m = 4$.
\begin{figure}[h]
\begin{center}
\begin{tikzpicture}[scale = 0.5]
  \draw[step = 1cm, black, thick](0,0) grid (4,4);
\draw[pattern=north west lines, pattern color=blue] (0,0) rectangle (1,1);
\draw[pattern=north west lines, pattern color=blue] (3,1) rectangle (2,2);
\foreach \x in {0,1,2,3}{
  \foreach \y in {0,1,2,3}{
  \draw[fill = red] (\x,\y) circle (2pt);
  } 
}
\end{tikzpicture}
\end{center}
\vspace{-0.25cm}
\caption{Tiling with squares for $m = 4$ and associated cells $C_{4}(0,0)$ and $C_{4}(2,1)$ (blue stripes) and red point of $\mathbb{G}_{m}$.}
\label{fig1}
\end{figure}

\paragraph{Discrete setting}
Using the previous square tiling, we write $S =  \underset{x \in \mathbb{G}_{m}}{\cup}  C_{m}(x)$. We assume to observe $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{G}_{m}}$, which we assume coincides with values of a stationary random field $\left(X_{\scriptscriptstyle x}\right)_{x \in \mathbb{Z}^{2}}$. The stationarity hypothesis means that for all $h \in \mathbb{Z}^{2}$, 
$$\left(X_{x+h}; x \in \mathbb{Z}^{2} \right)\overset{fdd}{=} \left(X_{\scriptscriptstyle x}; x \in \mathbb{Z}^{2} \right),$$ where $fdd$ denotes finite-dimensional distributions. \\
We denote by $\rho(x) :=\text{Cov}\left(X_{\scriptscriptstyle 0}, X_{\scriptscriptstyle x}\right), \; x \in \mathbb{Z}^{2}$, the covariance function of $X$.
\vspace{-1.5cm}
\begin{figure}[H]
    {\includegraphics[scale=0.25]{GaussianUn.pdf}}
    {\includegraphics[scale=0.25]{GaussianZUn.pdf}}
    {\includegraphics[scale=0.25]{GaussianZZZUn.pdf}}
    \vspace{-2cm}
 \caption{Generations of Gaussian random field with covariance $\rho(x) = e^{-\kappa||x||^{2}}$ with $m = 1024$, and different values for $\kappa$, from left to right $\kappa = 0.01, 0.1, 1$, using the Matlab function \textit{stationary Gaussian process} \cite{MATLAB}.}
\label{fig22}
\end{figure}
Let us consider a threshold parameter $t \in \mathbb{R}$. We introduce the associated binary image $Z^{\scriptscriptstyle (m)}_{t} = \left(\mathbbm{1}_{\left\{X_x \geq t\right\}} \right)_{x \in \mathbb{G}_{m}}$, each cell $C_{m}(x)$ is associated to black or white according to whether $Z^{\scriptscriptstyle (m)}_{t} (x) = 0$ or $Z^{\scriptscriptstyle (m)}_{t}(x)~= 1$. 
\subsection{Perimeter of a binary image}\label{methods}
For $t \in \mathbb{R}$,let $Z^{\scriptscriptstyle (m)} = Z^{\scriptscriptstyle (m)}_{t}$ be the  binary image  $Z^{\scriptscriptstyle (m)}$ at that given threshold $t \in \mathbb{R}$. Following  the approach  presented in \cite{HermineAgnes},  for each edge $w \in \mathbb{E}_{m}$, we aim to know if  $w$ contributes  to the perimeter of the black component of $Z$. Making use of the additive nature of the perimeter, one can start by computing the oriented perimeter given each direction, horizontal and vertical. Let us consider the edge $w_{i}(x) := \left(x, x+e_{i}\right)$ with $i \in \{1,2\}$, $w_{i}(x)$ belongs to $C_{m}(x) \cap C_{m}(x-e_{j})$ with $i,j \in \{1,2\}$ and $i \neq j$ as soon as $w_{i}(x) \subset  \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}$.
\begin{figure}[H]
\begin{center}
\begin{tikzpicture}
    [
        box/.style={rectangle,draw=black,thick, minimum size=1cm},
    ]

@@

\section{Statistics of the perimeter} 
\subsection{First moment}

@@

We assume that $\left(X_x \right)_{x \in \mathbb{G}_{m}}$ is a stationary Gaussian centered with unit variance random field let us denote \linebreak by  $\rho(e_i) = \text{Cov}\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) \in~[-1, 1]$. The expected value of the perimeter in \eqref{eq:6} is  given \linebreak by $$\mathbb{E}\left(\mathcal{P}_{m}(t)\right) = m(m-1)\sum_{1}^{2}\mathbb{E}\left(f^{(i)}(t) \right)$$  and

@@

\left\{ x \in \mathbb{G}_{m}; w_{i}(x) \in \mathbb{E}^{\scriptscriptstyle  (i)}_{m}\right\} & = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, (x, x+e_i)\subset (0,m)^{2} \right\} \\ 

@@

@@

 \text{if} \hspace{0.5cm} \tilde{\rho}(e_i) \leq \bar{\rho}(e_i) \hspace{0.5cm} \text{then} \hspace{0.5cm}\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(t)\right) \geq \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(t)\right).

@@

Let $t \in \mathbb{R}$ and $X$, $Y$ two centered with unit variance Gaussian random fields on $\mathbb{Z}^{2}$ of covariance stucture respectively $\tilde{\rho}$ and $\bar{\rho}$. We assume that $\tilde{\rho}(e_i) \leq \bar{\rho}(e_i)$, and consider the Gaussian vectors $\left(X_{0}, X_{e_1}\right)$ and $\left(Y_{0}, Y_{e_1}\right)$, $\tilde{\rho}(e_i) \leq \bar{\rho}(e_i)$ implies that $\mathbb{E}\left(X_{0}X_{e_1}\right) < \mathbb{E}\left(Y_{0}Y_{e_1}\right)$, we can write that

@@

\mathbb{P}\left(Y_{\scriptscriptstyle 0} < t \leq  Y_{e_1}\right) = \mathbb{P}\left(Y_{\scriptscriptstyle 0} < t\right) - \mathbb{P}\left(Y_{\scriptscriptstyle 0} < t,  Y_{e_1} < t\right),
according to Slepian's lemma, $\mathbb{P}\left(X_{\scriptscriptstyle 0} < t,  X_{e_1} < t\right) \leq \mathbb{P}\left(Y_{\scriptscriptstyle 0} < t,  Y_{e_1} < t\right)$, \linebreak besides,~$\mathbb{P}\left(Y_{\scriptscriptstyle 0} < t\right)=\mathbb{P}\left(X_{\scriptscriptstyle 0} < t\right)$ thus, 

@@

\mathbb{P}\left(Y_{\scriptscriptstyle 0} < t \leq  Y_{e_1}\right) \leq \mathbb{P}\left(X_{\scriptscriptstyle 0} < t \leq  X_{e_1}\right)
and,
\mathbb{P}\left(\min\left(Y_{\scriptscriptstyle 0}, Y_{e_1}\right) < t \leq \max\left(Y_{\scriptscriptstyle 0}, Y_{e_1}\right)\right)  \leq \mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_1}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_1}\right)\right) 
\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(t)\right) \geq \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(t)\right).

@@

Considering the contraposition of this result, we get the following 
 \text{if} \hspace{0.5cm}\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(t)\right) \neq \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(t)\right)   \hspace{0.5cm} \text{then}  \hspace{0.5cm} \tilde{\rho}(e_i) \neq \bar{\rho}(e_i) \hspace{0.5cm}.
\subsection{Covariance of the perimeter for two thresholds}

@@

& = \sum_{x_1=2-m}^{m-1} \sum_{x_2 = 1-m}^{m-2} \left(m-|x_1| - \mathbbm{1}_{x_{1} \leq 0}\right)\left(m-|x_2|-\mathbbm{1}_{x_{2} \geq 0}\right)\text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{ \scriptscriptstyle (2)}(x) \right)

@@

0 \leq x_2 \leq m-1 \\
0 \leq y_2 \leq m-1 
\end{array}\right. & \Leftrightarrow

@@

\text{Cov}\left(\mathcal{P}_{m}^{\scriptscriptstyle (1)}(t),\mathcal{P}_{m}^{\scriptscriptstyle (1)}(s) \right) &  = \sum_{z_{\scriptscriptstyle 1} = \left(2-m\right)}^{m-2}\sum_{z_{\scriptscriptstyle 2}=\left(1-m\right)}^{m-1}\left(m -1 -|z_{1}|\right)\left(m - |z_{2}|\right) \text{Cov}\left(f_{t}^{\scriptscriptstyle (1)}(0), f_{s}^{\scriptscriptstyle (1)}(z) \right) 

@@

\end{align*}}Let us assume that $|\rho(e_1)| < 1$, the Cholesky decomposition of $\tilde{\Sigma}_{i}(x)$ allows us to get the expression of the Gaussian vector $\left(\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0},\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle x},S^{\scriptscriptstyle (i)}_{\scriptscriptstyle x} \right)$ in a new basis $\left(U,V,W,Z\right)$ with $\left(U, V, W, Z\right) \sim \mathcal{N}\left(0,I_{4}\right)$. We get the following decomposition \\ 

@@

& = \mathbbm{1}_{\big\{ 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W  - |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \leq \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z} \\ 
& \hspace{3cm} _{\leq 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W + |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \big\}}

@@

&\hspace{-6.5cm} = \mathbb{E}\left(\mathbbm{1}_{\left\{ |2t - S^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}| \leq |\Delta^{\scriptscriptstyle (1)}_{\scriptscriptstyle 0}|\right\}}\mathbbm{1}_{\big\{ 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W  - |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \leq \pi^{\scriptscriptstyle(+, i)}_{Z}(x)Z} \right.  \\  
& \hspace{3cm}\left. _{\leq 2s -  \pi^{\scriptscriptstyle(+, i)}_{U}(x)U -  \pi^{\scriptscriptstyle(+, i)}_{V}(x) V -  \pi^{\scriptscriptstyle(+, i)}_{W}(x) W + |\Delta^{\scriptscriptstyle(i)}_ {\scriptscriptstyle x}| \big\}}\right)\\

@@

&\hspace{-6.2cm} \left. \left|\Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s + \left( \pi^{\scriptscriptstyle(-, i)}_{U}(x)- \pi^{\scriptscriptstyle(+, i)}_{U}(x)\right) U + \left(\pi^{\scriptscriptstyle(-, i)}_{V}(x)- \pi^{\scriptscriptstyle(+, i)}_{V}(x)\right)V + \left(\pi^{\scriptscriptstyle(-, i)}_{W}(x) - \pi^{\scriptscriptstyle(+, i)}_{W}(x)\right) W \right) \right. \right.  \nonumber \\
& \hspace{-6.5cm}\left. \left.  - \Phi_{ \pi^{\scriptscriptstyle(+, i)}_{Z}(x)}\left( 2s - \left( \pi^{\scriptscriptstyle(-, i)}_{U}(x)+ \pi^{\scriptscriptstyle(+, i)}_{U}(x)\right) U - \left(\pi^{\scriptscriptstyle(-, i)}_{V}(x)+ \pi^{\scriptscriptstyle(+, i)}_{V}(x)\right)V   - \left( \pi^{\scriptscriptstyle(+, i)}_{W}(x) +  \pi^{\scriptscriptstyle(-, i)}_{W}(x) \right)W \right)  \right| \right)

@@

\begin{tabularx}{\textwidth}{|P{3.5cm}|P{11.85cm}|}

@@

Variable & upper bound \\ \hline
